\documentclass[11pt, a4paper]{memoir}
\usepackage[english, science, dropcaps, hyperref, submissionstatement]{ku-frontpage}
\usepackage[utf8]{inputenc}



\usepackage{pdfpages}
\usepackage{mathrsfs}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{mathtools}
\DeclareMathOperator\arctanh{arctanh}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{centernot}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{braket}
\usepackage{lastpage}
\usepackage{enumitem}
\DisemulatePackage{setspace}
\usepackage{setspace}
\usepackage{xcolor}
\usepackage[english]{babel} 
\usepackage{dsfont}
\usepackage{appendix}
\usepackage{makecell}

\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing}
\newcommand{\tikznode}[3][inner sep=0pt]{\tikz[remember
	picture,baseline=(#2.base)]{\node(#2)[#1]{$#3$};}}
\usepackage{ytableau}

%\usepackage[T1]{fontenc}
%\usepackage{kpfonts}%  for math    
%\usepackage{libertine}%  serif and sans serif
%\usepackage[scaled=0.85]{beramono}%% mono


%\usepackage[sectionbib]{natbib}
\usepackage[square,sort,comma,numbers]{natbib}
%\usepackage[colorlinks=true,allcolors=blue]{hyperref}
%\usepackage[sectionbib]{bibunits}
%\defaultbibliographystyle{alpha}
%\defaultbibliography{bibliography}

\usepackage{fancyhdr}

\newcommand{\euler}[1]{\text{e}^{#1}}
\newcommand{\Real}{\text{Re}}
\newcommand{\Imag}{\text{Im}}
\newcommand{\supp}{\text{supp}}
\newcommand{\norm}[1]{\left\lVert #1 \right\rVert}
\newcommand{\abs}[1]{\left\lvert #1 \right\rvert}
\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\ceil}[1]{\left\lceil #1 \right\rceil}
\newcommand{\Span}[1]{\text{span}\left(#1\right)}
\newcommand{\dom}[1]{\mathcal D\left(#1\right)}
\newcommand{\Ran}[1]{\text{Ran}\left(#1\right)}
\newcommand{\conv}[1]{\text{co}\left\{#1\right\}}
\newcommand{\Ext}[1]{\text{Ext}\left\{#1\right\}}
\newcommand{\vertin}{\rotatebox[origin=c]{-90}{$\in$}}
\newcommand{\interior}[1]{%
	{\kern0pt#1}^{\mathrm{o}}%
}
\renewcommand{\braket}[1]{\left\langle#1\right\rangle}
\newcommand{\ketbra}[2]{\left\vert #1\middle\rangle\middle\langle #2 \right\vert}
\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand{\ie}{i.e. }
\newcommand{\eg}{e.g. }
\newcommand{\dd}{\partial }
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\w}{\mathsf{w}}
\newcommand{\rr}{\mathcal{R}}


\newcommand{\Gliminf}{\Gamma\text{-}\liminf}
\newcommand{\Glimsup}{\Gamma\text{-}\limsup}
\newcommand{\Glim}{\Gamma\text{-}\lim}

\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{definition}[theorem]{Definition}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{example}[theorem]{Example}

\numberwithin{equation}{section}

%\linespread{1.3}
\onehalfspacing


\setlength\arraycolsep{2 pt}
\setcounter{tocdepth}{2}
\setcounter{secnumdepth}{0}

\assignment{PhD thesis}
\author{Johannes Agerskov}

% The following are only needed if the \author, \title, \subtitle, and \date
% commands are not patchable. See the readme for more information.
\frontpageauthor{Johannes Agerskov}
\frontpagetitle{One Dimensional Dilute Quantum Gases and Their Ground State Energies}
%\frontpagesubtitle{An intruiging subtitle}
\frontpagedate{Submitted: March 31, 2023}

\title{One Dimensional Dilute Quantum Gases and Their Ground State Energies}
\subtitle{}
\date{Submitted: March 31, 2023}
\advisor{Advisor: Jan Philip Solovej}
%\frontpageimage{example.png}

\kupdfsetup{One Dimensional Dilute Quantum Gases and Their Ground State Energies}{}{Johannes Agerskov}

\interfootnotelinepenalty=10000

\begin{document}
	%\bibliographyunit[\chapter]
	\frontmatter
\begingroup
  \fontencoding{T1}\fontfamily{LinuxLibertineT-OsF}\selectfont
  \maketitle
\endgroup
\null\thispagestyle{empty}
\\
\hspace*{-1cm}{\textbf{Johannes Agerskov}\\
\hspace*{-1cm}QMATH\\
\hspace*{-1cm}Department of Mathematical Sciences\\
\hspace*{-1cm}University of Copenhagen\\
\hspace*{-1cm}\href{mailto:johannes-as@math.ku.dk}{johannes-as@math.ku.dk}\\
\hspace*{-1cm}\href{mailto:johannespwt@hotmail.com}{johannespwt@hotmail.com}
\vspace{5cm}

\hspace*{-1cm}\hspace{-0.88cm} \begin{tabular}{ll}
	Date of submission &\qquad March 31, 2023\\
	Date of defense &\qquad  June 6, 2023\\
	Advisor &\qquad  \makecell[tl]{\textbf{Jan Philip Solovej}\\ \ University of Copenhagen, Copenhagen, Denmark}\\
	Assessment committee &\qquad \makecell[tl]{\textbf{Søren Fournais} (Chair)\\
		\ University of Copenhagen, Copenhagen, Denmark\\
		\ Aarhus University, Aarhus, Denmark\\
	\textbf{Simona Rota Nodari}\\
	\ Université Côte d'Azur\\
	\ Nice, France\\
\textbf{Marcello Porta}\\
\ Scuola Internazionale Superiore di Studi Avanzati\\
\ Trieste, Italy }
	
\end{tabular}



\newpage
\begin{abstract}
	 In this thesis, we study the ground state energy of one dimensional dilute quantum systems with repulsive pair potentials. We review part of the general theory of many-body quantum mechanics. We then prove results describing conditions under which, we can associate a unique self-adjoint many-body Hamiltonian to certain repulsive pair-potential.\\
	 The point-interacting solvable models in one dimension, \ie the Lieb-Liniger and Yang-Gaudin models, are reviewed and certain results related to their ground state energy in the dilute limit are proved.\\
	 We proceed by proving a ground state energy expansion for the Bose gas. This is done by proving first an upper bound and next a matching lower bound. The ground state energy is found, up to next-to-leading order, to depend on the potential only through the scattering length. Thus the system exhibits universality similar to that observed for higher dimensional systems. Our result covers the well known results on the ground state energy of the Lieb-Liniger model in the Tonks-Girardeau (dilute) limit. However, our result allows for a very general class of potentials, including potential that differ significantly from the point interacting $ \delta $-potentials for example by having positive scattering length. As corollaries, we find similar result for spin polarized Fermi gases and gases with intermediate particle statistics, \ie anyons.\\
	 Finally we study the spin--$ 1/2 $ Fermi gas. Here we conjecture a ground state energy expansion based on the solvable models at hand. The upper bound from the bosonic case is generalized by realizing the spins, in a given trial state, to be described by an effective antiferromagnetic Heisenberg chain. Thereby, we prove an upper bound matching our conjecture. As corollaries, we find similar results for spin-$ 1/2 $ bosons and for fermions and particles with spatial symmetry with spin-dependent potentials. Furthermore, we generalize parts of the lower bound proof from the bosonic case, and prove in this case for spin--$ 1/2 $ fermions a lower bound related to the Lieb-Liniger-Heisenberg ground state energy. We notice that for spin-dependent potentials in certain regimes identified with a ferromagnetic phase, the lower bound is reduced to that of the Lieb-Liniger model. Thus a lower bound, matching the previous upper bound, is proved in the ferromagnetic phase for spin-dependent potentials. 
\end{abstract}
\newpage
\renewcommand*\abstractname{Resumé}
\begin{abstract}
	I denne afhandling studerer vi grundtilstandsenergien af endimensionelle fortyndede kvantegasser med frastødende parpotentialer. Vi opsummerer dele af den generelle teori omkring mangelegemekvantemekanik. Derefter beviser vi under hvilket betingelser en unik selvadjungeret mangelegeme Hamilton-operator kan associeres til et givet parpotentiale. De punktinteragerende løsbare modeller i én dimension, dvs. Lieb-Liniger og Yang-Gaudin modellerne, opsummeres og visse resultater relateret til deres grundtilstandsenergi i den fortyndede grænse bevises.\\
	Vi forsætter ved at bevise en udvikling af grundtilstandsenergien for Bose-gassen. Dette gøres ved at vise først en øvre begrænsning og derefter en matchende nedre begrænsning. Det vises at grundtilstandsenergien, til næstledende orden, kun afhænger af potentialet igennem spredningslængden. Dermed udviser systemet universalitet, som ligner den observeret i tilsvarende højeredimensionelle systemer. Vores resultat dækker det velkendte resultat vedrørende grundtilstandenergien af Lieb-Liniger modellen i Tonks-Girardeau grænsen, altså den fortyndede grænse. Dog holder vores resultat for mere generelle parpotentialer, inklusiv potentialer der afviger markant fra $ \delta $-potentialer ekspemelvis ved at have positiv spredningslængde. Som korollarer finder vi lignende resultater for den spin-polariserede Fermi-gas og gasser med mellemliggende partikelstatistikker, altså anyoner.\\
	Endeligt studederer vi spin--$ 1/2 $ Fermi-gassen. Her præsenterer vi, som en formodning, en udvikling af grundtilstandsenergien baseret på kendte løsbare modeller. Den øvre begrænsning fra det bosoniske tilfælde generaliseres ved at indse, at partiklernes spin, i en givet variationsbølgefunktion, kan beskrives ved en effektiv antiferromagnetisk Heisenberg-kæde. Dermed beviser vi en øvre begrænsning, der tilsvarer den fremsatte formodning. Som korollarer finder vi lignende resultater for spin--$ 1/2 $ bosoner og for fermioner og partikler med rumlig symmetri med spin-afhængige potentialer. Ydermere generaliserer vi dele af beviset for den nedre begrænsning fra det bosoniske tilfælde, og vi beviser i dette tilfælde en nedre begrænsning for spin--$ 1/2 $ fermioner, der relaterer grundtilstandsenergien til dén fra Lieb-Liniger-Heisenberg modellen. Vi bemærker, at for spin-afhængige potentialer i visse regimer, som vi identificerer med en ferromagnetisk fase, reducerer den nedre begrænsing til dén af Lieb-Liniger modellen. Dermed bevises en nedre begrænsning, der matcher den førviste øvre begrænsning i netop den ferromagnetiske fase for spin-afhængige potentialer.
\end{abstract}

\newpage
\renewcommand*\abstractname{Acknowledgements}
\begin{abstract}
	As my time as a PhD student is coming to an end, there are many people to whom I am grateful. First and foremost, I would like to thank my advisor, Jan Philip Solovej, for introducing me to the field of dilute quantum gases, his exceptional advice, a good collaboration, and many interesting and very enjoyable discussions. It has been a pleasure being his student over the last three and a half years.\\
	I would also like to express my gratitude to Robin Reuvers for a good collaboration and many interesting and enjoyable discussions.\\
	Next, I would like to thank all of the members of QMATH over the last three and a half years for the good company both in and outside of the office. Special thanks go to Mads, Marie, Jacob, and August for being great coffee break buddies and for discussing a wide variety of subjects that includes, but does not restrict to, mathematics and physics.\\
	Also many thanks to Jacob Fronk and Lukas Junge for giving feedback on parts of this thesis.\\
	I am grateful to Robert Seiringer for valuable discussions during my visit to IST Austria and to IST Austria for the hospitality.\\
	I also thank my family, and my dad in particular, for all the encouragement, and my son for making me smile and laugh so very often.\\
	Finally, no one deserves my gratitude more than my fiancée, Martina, who has been ever supportive, through thick and thin, for the last almost ten years.
\end{abstract}
\renewcommand*\abstractname{Abstract}


\newpage
\tableofcontents
\newpage
\begin{center}
\large{\textbf{Preprint Included as Part of This Thesis}}\\
\normalsize

\begin{itemize}
\item[\cite{agerskov2022ground}]	Ground state energy of dilute Bose gases in 1D,\\
	 	\emph{Johannes Agerskov, Robin Reuvers, and Jan Philip Solovej,\\
	 	ArXiv, arXiv:2203.17183}\\
 	\footnotesize{\textbf{This preprint was revised and edited before being included in this thesis.}}
 	\normalsize
\end{itemize}
\end{center}

\mainmatter
\include{Chapters/Introduction}
\include{Chapters/Many-Body_Quantum_Mechanics}
\include{Chapters/The-Ground-State-Energy-Bose-Gas}
\include{Chapters/The-Ground-State-Energy-Fermi-Gas}
\include{Chapters/Conclusion-and-Outlook}
\include{Chapters/Appendices}

\bibliographystyle{alpha}
\bibliography{bibliography}

\end{document}
