\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{pdfpages}
\usepackage{mathrsfs}
\usepackage{amsfonts}
\usepackage{amsmath}
\DeclareMathOperator\arctanh{arctanh}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{centernot}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{braket}
\usepackage{pgfplots}
\usepackage{lastpage}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{xcolor}
\usepackage{cancel}
\usepackage{scrextend}
\usepackage[english]{babel} 

\usepackage[square,sort,comma,numbers]{natbib}
\usepackage[colorlinks=true,linkcolor=blue]{hyperref}

\usepackage{fancyhdr}
\newcommand{\euler}[1]{\text{e}^{#1}}
\newcommand{\Real}{\text{Re}}
\newcommand{\Imag}{\text{Im}}
\newcommand{\supp}{\text{supp}}
\newcommand{\pare}[1]{\left( #1 \right)}
\newcommand{\norm}[1]{\left\lVert #1 \right\rVert}
\newcommand{\abs}[1]{\left\lvert #1 \right\rvert}
\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\Span}[1]{\text{span}\left(#1\right)}
\newcommand{\dom}[1]{\mathscr D\left(#1\right)}
\newcommand{\Ran}[1]{\text{Ran}\left(#1\right)}
\newcommand{\conv}[1]{\text{co}\left\{#1\right\}}
\newcommand{\Ext}[1]{\text{Ext}\left\{#1\right\}}
\newcommand{\vin}{\rotatebox[origin=c]{-90}{$\in$}}
\newcommand{\interior}[1]{%
	{\kern0pt#1}^{\mathrm{o}}%
}
\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand{\ie}{\emph{i.e.} }
\newcommand{\eg}{\emph{e.g.} }
\newcommand{\dd}{\partial }
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\w}{\mathsf{w}}

\newcommand{\Gliminf}{\Gamma\text{-}\liminf}
\newcommand{\Glimsup}{\Gamma\text{-}\limsup}
\newcommand{\Glim}{\Gamma\text{-}\lim}
\newcommand{\pipe}{\ \vert \ }

\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\numberwithin{equation}{section}
\linespread{1.3}

\pagestyle{fancy}
\fancyhf{}
\rhead{CoCo - Assignment 5}
\lhead{}
\rfoot{\thepage}
\lfoot{Dated: \today}
\author{Johannes Agerskov, Mads Friis Frand-Madsen, and Sifan Huang}
\date{Dated: \today}
\title{CoCo - Assignment 5}
\begin{document}

\maketitle
\section*{7.7}
We show that NP is closed under union and concatination.\begin{proof}
	We start by considering union. Let $ A,B\in \text{NP} $ and consider $ L=A\cup B $. We construct a polynomial time verifier for $ L $. We know that there exist polynomial time verifiers $ V_A $ and $ V_B $ for $ A $ and $ B $. Now Consider the verifier $ V $ that on input $ \braket{w,c} $, run $ V_A $ and $ V_B $ on $ \braket{w,c} $ and if one of them accepts, $ V $ accepts, otherwise it rejects. This is clearly polynomial in time, since it is just two polynomial time verifiers in series. Also $ V $ accepts $ w $ for some $ c $ if and only if $ w\in A $ or $ w\in B $ or equivalently if and only if $ w\in L=A\cup B $.\\
	 For the concatenation, let $ L'=AB $. We construct polynomial time verifier $ V' $ such that $ V' $ verifies $ L' $. A certificate, $ c $, in this case, is an encoding of three things: Where to split the input $ w $, a certificate for $ V_A $ on the left part, and a certificate for $ V_B $ on the right part. Given such a $ c=(\braket{k},c_A,c_B) $, where $ \braket{k} $ denotes a suitable encoding of the number $ k $, and input $ w=w_1...w_n $, $ V' $ acts as following on input $ \braket{w,c} $: $ V' $ splits the input, $ w $, at the $ k $th position, according to the certificate, $ c $. It then runs $ V_A $ on $ w_1...w_k $ with certificate $ c_A $ and $ V_B $ on $ w_{k+1}...w_n $ with $ c_B $. If both accept $ V' $ accepts. Clearly, $ V' $ accepts $ w $ for some $ c $ if $ w\in L'=AB $. On the other hand, if $ V' $ accepts $ w $ for some $ c $ there exist a splitting of $ w $ such that the left part is in $ A $ and the right part is in $ B $ or equivalently, $ w\in L'=AB $
\end{proof}

\section*{7.9}
We show that $ TRAINGLE=\{\braket{G}\ \vert\ G\text{ is an undirected graph that contains a }3\text{-clique}\} $ is in P.
\begin{proof}
	We consider the following algorithm. $ D= $"On input $ \braket{G} $\begin{enumerate}
		\item check that $ \braket{G} $ encodes an udirected graph. (say with vertices $ v_1,...,v_n $)
		\item For $ i=1 $ to $ n-2 $ select $ v_i $ and:
		\item \qquad For $ j=i+1 $ to $ n-1 $ select $ v_j $ and:
		\item \qquad \qquad For $ k=j+1 $ to $ n $ select $ v_k $ and:
		\item \qquad\qquad\qquad Check that $ \{v_i,v_j,v_k\} $ forms a $ 3 $-clique. If true accepts. If false and $ i=n-2 $, $ j=n-1 $ and $ k=n $, reject."
	\end{enumerate}
	Since there are $ \frac{n(n-1)(n-3)}{6}=O(n^3) $ ways to choose $ 3 $ vertices out of $ n $ and each selection process if polynomial in time, this algorithm is clearly polynomial in time. It is also clear that the algorithm accepts if and only if $ G $ contains a $ 3 $-clique (Triangle).\\
	Notice that we use that for any reasonable encoding of a $ \braket{G} $ the input length is polynomial in the number of vertices.
\end{proof}

\section*{7.10}
We show that $ ALL_{DFA}=\{\braket{A}\ \vert\ A\text{ is a DFA and }L(A)=\Sigma^* \} $ is in P.
\begin{proof}
	We show this, by noting that $ ALL_{DFA} $ can be solved with the TM, $ M $ from the proof that $ PATH $ is in P. Simply construct the TM, $ M'= $"On input $ \braket{A} $\begin{enumerate}
		\item Construct the state diagram, $ G $ of $ A $, vieved as a directed graph.
		\item For all states $ q\in Q\setminus F $ ($ F $ is the set of accepts states of $ A $), run $ M $ on $ \braket{G,q_{\text{start}},q} $, if it accepts for some $ q $, \emph{reject} if it rejects for all $ q $, \emph{accept}.
	\end{enumerate}
	Evidently, $ M' $ accepts exactly those DFAs that can never reach a non-accepts state, \ie those that accept the language $ \Sigma^* $. Since $ PATH $ is in P, $ M $ runs in polynomial time, $ \braket{G,q_{\text{start}},q} $ is polynomial in the input length, $ \abs{\braket{A}} $, and since the set $ Q $ is polynomial in the input length, we conclude that $ M' $ is a polynomial time TM that accepts $ ALL_{DFA} $.
\end{proof}

\section*{7.42}
We show that P is closed under the star operation.
\begin{proof}
	Let $ A $ be any language in P. We follow the hint, and construct a polynomial time TM that accepts $ A^* $. Let $ D $ be the polynomial time TM that accepts $ A $, and let $ M $ be the polynomial TM that accepts $ PATH $. Consider then, $ M'= $"On input $ y=y_1...y_n $
	\begin{enumerate}
		\item Build $ n\times n $-table, with entries $ T_{i,j} $, for $ i,j=1,...,n $, by the following procedure:\\
		For $ i=1 $ to $ n $
		\item\qquad For $ j=i $ to $ n $
			\item\begin{addmargin}[4em]{0em} Run $ D $ on $ y_i...y_j $, if it accepts, set $ T_{ij}=1 $, if it rejects set $ T_{ij}=0 $. For $ i>j $ set $ T_{ij}=0 $.
				\end{addmargin}
		\item Let $ G $ be the directed graph with adjacency matrix $ T $, \ie view $ \braket{T_{ij}}_{i,j=1}^{n} $ as an encoding of the graph $ G $ (we label the vertices of $ G $ by $ 1,...,n $).
		\item Run $ M $ on $ \braket{\braket{T_{i,j}}_{i,j=1}^{n},1,n} $, if it accepts, \emph{accept}, if it rejects, \emph{reject}. 
	\end{enumerate}
	By design, we that $ M' $ accepts $ y $ if and only if there is a path $ 1\to i_1\to i_2\to...\to i_l\to n $ such that $ T_{1,i_1}=T_{i_j,i_{j+1}}=T_{i_l,n}=1 $ for all $ j=1,...,l $, which is equivalent to $ y_1...y_{i_1}\in A $, $ y_{i_j}...y_{i_j+1}\in A $, and $ y_{i_l}...y_{n}\in A $ for all $ j=1,...,l $, or equivalently that $ y\in A^* $. Furthermore, we see that all steps are polynomial time the input length, and the number of steps is also polynomial in the input length from which we conclude that $ M' $ is a polynomial time TM that accepts $ A^* $. 
\end{proof}

\section*{7.44}
Let $ UNARY\text{-}SSUM $ be the subset sum problem where all numbers are represented in unary numbers.
\begin{proof}
	We describe an algorithm that accepts $ UNARY\text{-}SUM $ in polynomial time. Let $ M $ be an algorithm that solves the SUBSET-SUM problem in exponential time, which is known to exist, since $ SUBSET-SUM $ is in NP  by Theorem 7.25, and by Theorem 7.20 there then exist a non-deterministic TM that decides it in polynomial time $ O(n^m) $ for some $ m\geq 1 $, and then by Theorem 7.11 there exist a deterministic single tape TM that desides it in exponential time ($ 2^{O(n^m)} $). Consider $ D= $" on input $ \braket{\{i_1,...,i_n\},t} $ where $ i_1,...,i_n,t $ are unary numbers\begin{enumerate}
		\item For all $ j=1 $ to $ n $: Encode $ i_j $ as a binary number, $ b_j $, by straightforwardly starting with $ b_j=0 $ and then updating $ b_j $ while reading across $ i_j $. \eg $ i_j=1111 $ we would have $(b_j=0,\ 1111)\to (b_j=1,\ \dot{1}111)\to (b_j=10,\ \dot{1}11)\to (b_j=11,\ 11\dot{1}1)\to (b_j=100,\ 111\dot{1}) $, where the dot, symbolises the current position of, say the tape head in a TM. 
		\item Encode $ t $ as a binary $ \tilde{t} $ by same proceedure as in step 1. 
		\item For each subset of $ \{b_1,...b_n\} $, $ I $, calculate the sum of $ I $, and check if it equals $ \tilde{t} $.
	\end{enumerate}
	Notice that the input length of $ M $ in the above algorithm $ \abs{\braket{\{b_1,...,b_n\},\tilde{t}}}=O(\log(\abs{\braket{\{i_1,...,i_n\},t}})) $. Thus $ M $ will run in time $ 2^{O(\log(n)^m)}\leq2^{c\log(n)^m}\leq=n^c $ for some $ c $, thus it runs in polynomial time. Clearly converting unary to binary is also polynomial in time. Thus $ D $ runs in polynomial time, and accepts exactly $ UNARY\text{-}SSUM $. 
\end{proof}
\begin{proof}
	We describe an algorithm that accepts $ UNARY\text{-}SUM $ in polynomial time. Let $ A $ be any language in P, and let $ M_A^* $ be the algorithm from 7.42, that desides $  A^*  $ in polynomial time. Now given an input $ \braket{\{i_1,...,i_n\},t} $ where $ i_1,...,i_n,t $ are unary, we notice that $ \{i_1,...,i_n\} $ is trivially a language in P, \eg because membership can be checked by trial an error or because it is context free. Now consider the algorithm $ D= $" on input $ \braket{A,t} $ where $A=\{i_1,...,i_n\}$, and $ i_1,...,i_n,t $ are unary\begin{enumerate}
		\item Run $ M_{A^*} $ on $ t $, if it accepts, \emph{accept}, if it rejects, \emph{reject.}
	\end{enumerate}
	Clearly, $ D $ accepts $ \braket{\{i_1,...,i_n\},t} $ if and only if $ t=i $
\end{proof}

Let $ UNARY\text{-}SSUM $ be the subset sum problem where all numbers are represented in unary numbers. We show that $ UNARY\text{-}SSUM $ is in P.
\begin{proof}
	Consider the CFG, $ G $:\begin{equation*}
	\begin{aligned}\\
	S&\to A\vert B\\
	A&\to 1A1\vert \# B\vert \$\\
	B&\to1B\vert \#B\vert \#A\vert \$
	\end{aligned}
	\end{equation*}
	By inspection, it is clear that this CFG can produce strings of the form $ u_1\#...\#u_m\$u $ where for some $ 1\leq i_1<...<i_k\leq m $, we have $ u_{i_1}...u_{i_k}=u $, \eg $ 111\#11\#111111\#1\$1111 $. This is easily seen from the fact that we can produce a $ 1 $ to the right of $ \$ $ only by producing one to the left of $ \$ $ as well, furthermore, one can only stop producing $ 1 $s to the right of $ \$ $ by putting down a $ \# $ on the left. However, this language is clearly equivalent to $ UNARY\text{-}SSUM $, by the bijective the map $ \braket{\{u_1,...,u_m\},u}\mapsto \braket{u_1\#...\#u_m\$u} $ which is clearly both polynomial time comptable and its inverse is also polynomial time computable. Thus we conclude that $ UNARY\text{-}SSUM\leq_P L(G) $, but by theorem 7.16 $ L(G) $ is in P, and thus by Theorem 7.31 $ UNARY\text{-}SSUM $ is in P.
\end{proof}


\section*{Exam 2019, Question 3}
\subsection*{3.1}
\begin{equation*}
	\begin{aligned}
	i\text{-}RSP=\left\{\braket{G}\ \vert\ \text{G}\text{ is a graph and there exist tree subgraph $ T\subset G $ such that $ V(T)=V(G) $,}\right.\\\left.\text{ and for any vertex in $ T $ the degree is 0, 1, or $ i $} \right\} 
	\end{aligned}
\end{equation*}
\subsection*{3.2}
We show that $ 3\text{-}RSP $ is NP-complete.\begin{proof}
	We do this by reducing the NP-complete problem $ UHAMPATH $ to $ 3\text{-}RSP $. Consider the algorithm, $ D= $"On input $ \braket{G,s,t} $ where $ G $ is a graph and $ s,t $ are vertices in $ G $\begin{enumerate}
		\item Construct the graph $ G' $ such that $ G\subset G' $ by adding one vertex $ b_i $ to $ G $ for every vertex $ v_i\in G\setminus{s,t} $ where we identify $ V(G)=\{v_1,...,v_m,s,t\} $, and add one line between each $ v_i $ and $ b_i $.
	\end{enumerate}
	this is clearly polynomial in time. Furthermore, notice that if $ G $ has a Hamiltonian path from $ s $ to $ t $, then $ G' $ has a 3-regular spanning tree, since the path from $ s $ to $ t $ go through all $ v_i $ exactly once, and by adding the lines from $ v_i $ to $ b_i $ we see that the vertices $ \{v_1,...,v_m,b_1,...,b_m,s,t\} $ with the lines given by the Hamiltonian path from $ s $ to $ t $ and the lines from $ v_i $ to $ b_i $ forms a 3-regular spanning tree, such that $ v_i $ has degree $ 3 $ for all $ i=1,...,m $ and $ \{s,t,b_1,...,b_m\} $ are the leaves of degree $ 1 $. On the contrary, if $ G' $ has a 3-regular spanning tree, we see that $ \{b_1,...,b_m\} $ must be leaves since they have degree $ 1 $. Hence $ \{v_1,...,v_m\} $ has degree 3, but since $ s,t $ only connects to $ \{v_1,...,v_n\} $ they must themselves be leaves. Notice then that $ s $ and $ t $ actually must be at the bottom of the tree, since any $ v_i $ exept the bottom one can have at most $ 1 $ leaf, since they have degree $ 3 $. Thus a Hamiltonian path from $ s $ to $ t $ exist by going from $ s $ up the tree all the way to the root, and down the other branch all the way down to $ t $ at the bottom. This path goes through every vertex $ v_1,..,v_m $ exactly once. Therefore, we see that $ D $ maps $ UHAMPATH $ to $ 3\text{RSP} $ and $ \overline{UHAMPATH} $ to $ \overline{3\text{-}RSP} $. Thus the map $ G\mapsto G' $ is a polynomial time computable function, and we conclude that $ UHAMPATH\leq_P 3\text{-}RSP $ by Theorem 7.36 that $ 3\text{-}RSP $ is NP-complete.\\
	Lastly we also need to show that $3\text{-}RSP  $ is in NP. This is done by constructing a polynomial time verifier for $ 3\text{-}RSP $. First notice that one may easily check, in polynomial time, wether a graph is connected. Simply mark one vertex, and the mark all unmarked vertices that this vertex connect to, search for an unmarked vertex that connect to a marked one, and mark then this one, an iterate until no more vertices can be marked. If all are marked accept, if some are unmarked, reject. Run time for this algorithm is polynomially bounded since, every iteration requires at most $ n $ markings, where $ n $ is the number of vertices, the search requires at most $ n $ moves and we must repeat at most $ n $ times, thus we can do this in $ O(n^3) $ time. To check if a graph is a tree, we simply remove each line one at a time, and check if the graph is still connected, which can be done in polynomial time, since there are at most $ n(n-1)/2 $ lines in the graph (we assume no lines from $ v $ to $ v $ for any vertex $ v $). If the graph is still connected after some line is remove, reject, if is it disconnected for every line, accept. Clearly this also runs in polynomial time. Thus we may in polynomial time check if a graph is a connected tree. The degree of all the vertices may also be checked in polynomial time, since there are $ n $ vertices and at most $ n-1 $ lines for each vertex. Thus we construct the verifier "$ V(G,c)= $On input $ \braket{G,c} $ where $ G $ and $ c $ are graphs\begin{enumerate}
		\item Check that $ V(c)=V(G) $. If not reject.\\
		\item Check that $ c $ is a connected 3-regular tree. is yes, accepts, else reject.
	\end{enumerate}
	This is clearly a polynomial time verifer, and it clearly accepts $ G $ for some $ c $ if and only if $ G \in 3\text{-}RSP$."
\end{proof}
\end{document}